%\vspace*{-0.15in}
%\hrule
%\vspace{0.2in}

\subsection*{\textsc{Computational Materials Scientist}}
\begin{itemize}[noitemsep]
 \item \emph{Scientist} at Karlsruhe Institute of Technology \hfill{Jul 2017-present}
\begin{itemize}[topsep=0pt] \setlength\itemsep{-0.1cm}
	\item Providing computational insights on the novel cluster-assembly approach to metallic glasses.
	\item Innovated physics-based models for the research projects.
	\item Development of HPC simulation software modules (using LAMMPS, Python and Git).
	\item Utilized supercomputers to perform  calculations with said modules.
	\item Devised project-specific algorithms to reduce simulation times by upto 50\%.
	\item Created post-processing tool-kit in Python for spatial-/time-based data sets (using numpy, matplotlib, OVITO, scipy, sk-learn APIs).
\end{itemize}
\item \emph{Visiting Researcher} at University of California, Irvine \hfill{Jan-Feb 2020}
\begin{itemize}[topsep=0pt]  \setlength\itemsep{-0.1cm}
\item Worked with stochastic methods to improve my simulation models. %\\(Monte-Carlo \& Autonomous Basin Climbing) 
\item Successfully established a research collaboration. 
\end{itemize}

%\vspace{0.2 cm}
\end{itemize}

\subsection*{\textsc{Research Scientist}}
\begin{itemize}[noitemsep]
\item School of Physics, University of Hyderabad \hfill {Nov 2016-Jun 2017}
\begin{itemize}[noitemsep,topsep=0pt]
%\item Wrote a successful national level grant proposal to secure funding.
\item Developed Scilab (open-source v. MATLAB) scripts to predict material properties using an empirical physics-based model, and compare with quantum-accurate calculations using CASTEP on Materials Studio.
\item Teaching Assistant for a master's level course titled 'Experimental Methods'.
\item Supervised a master's thesis student.
\end{itemize}\item School of Physics, University of Hyderabad \hfill {Jul-Nov 2016}
%On \emph{"Discovery of low dimensional quantum systems and geometrically frustrated materials"}
\begin{itemize}[noitemsep,topsep=0pt]
\item Synthesized and characterized complex magnetic materials.
\item Wrote Scilab scripts to automate non-linear data fitting and data plotting.
\end{itemize}
%\vspace{0.2 cm}
\end{itemize}

\subsection*{\textsc{Summer Research Scholar}}
Worked with C++ scripting, data-analysis, scientific equipment instrumentation and interfacing, graphical programming in various projects at:
\begin{itemize}[noitemsep]

\item Dept. of Physics, National University of Singapore \hfill {May-Jul 2015}\\
On \href{http://syamalpraneeth.weebly.com/uploads/9/5/9/2/95928492/nus.pdf}{\emph{"Study of ferroelectric transitions in $BaSn_{x}Ti_{1-x}O_{3}$"}}

%\vspace{0.2 cm}
\item Dept. of Physics, Indian Institute of Technology-Madras \hfill {May-Jul 2014} \\
On \href{http://syamalpraneeth.weebly.com/uploads/9/5/9/2/95928492/iitm.pdf}{\emph{"Calculations of Magnetic Field due to a Helmholtz Coil"}} 
%\\
%\vspace{0.2 cm}

\item Dept. of Physics, University of Wisconsin-Madison \hfill {May-Jul 2013}\\
On \href{http://syamalpraneeth.weebly.com/uploads/9/5/9/2/95928492/uwm.pdf} {\emph{"$\tau^{-} \tau^{+}$ Analysis for Decay of Neutral Heavy Higgs in two Higgs Doublet Model"}} 
%% \vspace{0.2 cm}

\end{itemize}

%\vspace{-0.4cm}
