\subsection*{Journal Articles}
$^*$Publications relevant to this thesis.

\begin{itemize}%[noitemsep]
\item \textsf{{Cluster Size effects in Cluster-based Glasses$^*$}}\\
S. P. Chilakalapudi, A. Sarkar, and H. Hahn, (in preparation). %\underline{S. P. Chilakalapudi}

\item \textsf{Energetically Deposited Cluster Assembly of Metallic Glasses$^*$}\\
S. P. Chilakalapudi, S. Katnagallu, A. Sarkar, P. Cao, W. Wenzel, and H. Hahn, \textit{Acta Materialia} (2022), 118152, \texttt{\href{https://doi.org/10.1016/j.actamat.2022.118152}{https://doi.org/10.1016/j.actamat.2022.118152}}.

\item \textsf{Geometrical frustration in a new $S=\frac{1}{2}$ distorted checkerboard lattice PbCuTeO$_5$}\\
S. P. Chilakalapudi, A. Shahee, A. V. Mahajan, S. Srinath, and B. Koteswararao, \textit{AIP Conf. Proc.} \textbf{1832}, 130032 (2017) \texttt{\href{https://doi.org/10.1063/1.4980752}{https://doi.org/10.1063/1.4980752}}.

\item \textsf{Synthesis and magnetic properties of a quantum magnet PbCuTeO$_5$}\\
B Koteswararao, S. P. Chilakalapudi, A. Shahee, P. V. Srinivasarao, S. Srinath, A. V. Mahajan, arXiv preprint, \texttt{\href{https://doi.org/10.48550/arXiv.1705.10560}{https://doi.org/10.48550/arXiv.1705.10560}}
\end{itemize}

%\subsection*{Pre-prints}
%\begin{itemize}
%\item \textsf{Synthesis and magnetic properties of a quantum magnet PbCuTeO$_5$}\\
%B Koteswararao, S. P. Chilakalapudi, A. Shahee, P. V. Srinivasarao, S. Srinath, A. V. Mahajan, arXiv preprint, \texttt{\href{https://doi.org/10.48550/arXiv.1705.10560}{https://doi.org/10.48550/arXiv.1705.10560}}
%\end{itemize}
\subsection*{Conference contributions}
$^*$Presenting author \\

\underline{Oral Presentations}
\begin{itemize}%[noitemsep]
	\item \textsf{Local Structure Tailoring In \cz Cluster-assembled Metallic Glasses}\\
	S. P. Chilakalapudi$^*$, S. Katnagallu, P. Cao, W. Wenzel, and H. Hahn, DPG Spring Meeting, Mar 2021.
	
	\item \textsf{Geometrical frustration in a new $S=\frac{1}{2}$ distorted checkerboard lattice PbCuTeO$_5$}\\
	S. P. Chilakalapudi$^*$, A. Shahee, A. V. Mahajan, S. Srinath, and B. Koteswararao, International Conference on Magnetic Materials (ICMAGMA), Hyderabad, Feb 2017.
\end{itemize}

\underline{Poster Presentations}
\begin{itemize}%[noitemsep]
	\item \textsf{Cluster-assembly of Metallic Glasses as a means to Local Structure Tailoring in Amorphous Materials}\\
	S. P. Chilakalapudi$^*$, S. Katnagallu, A. Sarkar, P. Cao, W. Wenzel, and H. Hahn, CECAM Workshop on Virtual Materials Design, Jul 2021.
	
	\item \textsf{Controlling the structure and properties of cluster-assembled amorphous materials} \\
	C. Benel$^*$, S. P. Chilakalapudi$^*$, A. Leon, T. Reisinger, L. Henrichs, R. Kruk, K. Fink, W. Wenzel, H. Hahn, POF, Karlsruhe, Sep 2018.
	
	\item \textsf{Synthesis and characterization of a new $S=\frac{1}{2}$ distorted checkerboard lattice PbCuTeO$_5$}\\
	S. P. Chilakalapudi$^*$, S. Srinath, and B. Koteswararao, Frontiers in Physics symposium, Hyderabad, Dec 2016.
	
	\item \textsf{Synthesis and characterization of a new $S=\frac{1}{2}$ distorted checkerboard lattice PbCuTeO$_5$}\\
	S. P. Chilakalapudi$^*$, A. Shahee, A. V. Mahajan, S. Srinath, and B. Koteswararao, 61$^{st}$ DAE Solid state physics symposium, Bhubaneshwar, Dec 2016.
\end{itemize}

