\chapter{Acknowledgments} \label{c:ack}
The success of my Ph.D. work and this dissertation has been made possible by many benefactors, and I would like to thank each and every one of them. \par

Firstly, I gratefully acknowledge the support and guidance from Prof. Horst Hahn---my supervisor. His enthusiasm for my scientific problem, and his confidence in me especially during difficult periods of my doctoral journey were instrumental to the progress and successful completion of this work. \par

I thank Prof. Karsten Albe for willing to be co-review my thesis, and even more importantly for his many delightful works on the simulations of metallic glasses and nanoglasses, which greatly influenced and inspired my scientific thought. \par

Prof. Penghui Cao was present to discuss my research problems when I needed him, and played the perfect host for my short research stay at UC Irvine. I thank him for the stimulating scientific discussions and a very wonderful research collaboration. I also thank Prof. Wolfgang Wenzel for the important initial discussions of my project, and for supporting my proposals to get access to high performance computing resources. \par

I greatly appreciate the useful discussions and advise from Prof. Sree Harsha Nandam, Dr. Shyam Katnagallu, Dr. Abhishek Sarkar and Dr. Robert Kruk from the Hahn group, and from Dr. Modan Liu, Dr. Manuel Konrad and Dr. Saientan Bag of the Wenzel group. For lending me a patient ear to discussing my work (scientific and administrative) challenges, to helping me build LAMMPS initially on my machine, to giving me constructive feedback on my research progress, and being available to discuss my ideas with---to being the kind and supportive mentors that I strive to become: thank you all very much. \par

I am also thankful to Dr. Omar Adjaoud, for useful discussions on nanoglasses in the final stages of my doctoral work. I acknowledge the effective proof-reading and criticism of this dissertation by Dr. Abhishek Sarkar, Prof. Harsha Nandam, Dr. Robert Kruk, Dr. Saientan Bag, Dr. Surya Abhishek Singaraju and Dr. Nithin Suryadevara. \par

My association with both the Hahn group and Wenzel group helped me form good friendships at the \gls{int}. I value the lunches and coffee breaks, dinners, and in general the friendship of Gleb Iankevich, David Stenzel, Felix Neuper, Nicolas Gack, Ruby Singh, Montserrat Pe\~naloza-Amion, Dr. Saibal Jana, Manuel Rommel, Dr. J\"org Schaarschmidt, and Dr. Tobias Schl\"oder. Our trips together, including the LaClusaz and Virtmat retreats are very memorable. \par

I greatly benefited from the administrative support from Ms. Christine Fischer, Ms. Patricia Jaeger and Ms. Birgit Limmer, who ensured that my time at the \gls{int} was comfortable and productive. Between the changes of my workstations and resolving Linux issues, I got a lot of IT-support from Mr. Thomas Koch, Mr. Daniel Lerch and Mr. Michael Birkel-Suck. I am grateful to Marei Peischl of peiTex TEXnical Solutions for the \tex  advice to typeset this dissertation. \par

I wish to also thank all the others whom I have mistakenly forgotten to mention here. \par

I thank all my friends and \textit{fraandz} Dr. Surya Abhishek, Dr. Nithin Suryadevara, Dr. Vamsi Manthena, Dr. Sukeert and Dr. Sahana Sheshachala for all the warmth and support. \par 

I am extremely fortunate for having such a wonderful family, who has always encouraged me, and has made endless sacrifices to aid my success in all my endeavours. I thank my late grandfather(/{\tel తాతగారు}) for buying me lots of books and sparking my interest in science and literature. I am lucky to have had my brother Prabhath for all the silly inside jokes during stressful times and for being my thesis writing work-buddy. I am overwhelmed with gratitude towards my parents Vasantha and Dasaratha Ram for their unfailing belief in my capabilities. I owe much of my success to my father, for he was often also the career coach that I needed. I am grateful to my wife Sunayana for her unwavering support, and I treasure the comfort that her presence brings to my life.

\clearpage